%% -*- LaTeX -*-

\begin{classpage}{Duration}

A class to store time spans.

\mansection{Synopsis}
\begin{mansynopsis}
#include <lisle/Duration>

class Duration
{
public:
  ~Duration ();
  Duration ();
  Duration (const Duration& that);
  Duration& operator = (const Duration& that);
  Duration (double seconds);
  int64_t sec () const;
  uint32_t nsec () const;
  Duration operator - () const;
  bool operator == (const Duration& that) const;
  bool operator != (const Duration& that) const;
  bool operator < (const Duration& that) const;
  bool operator > (const Duration& that) const;
  bool operator <= (const Duration& that) const;
  bool operator >= (const Duration& that) const;
  Duration& operator += (const Duration& that);
  Duration& operator -= (const Duration& that);
};
Duration operator + (const Duration& lho, const Duration& rho);
Duration operator - (const Duration& lho, const Duration& rho);
\end{mansynopsis}

\mansection{Description}
\begin{mandescription}
  \destructor
  Destroys \farg{this} duration.
  
  \constructor{}
  Constructs \farg{this} duration as a zero time span.
  
  \constructor{const Duration\& \farg{that}}
  Constructs \farg{this} duration from \farg{that} duration.
  The time span stored in \farg{that} is copied into \farg{this}.
  
  \operator{Duration\&}{=}{=}{const Duration\& \farg{that}}
  Assigns \farg{that} duration to \farg{this} duration.
  The time span stored in \farg{that} is copied into \farg{this}.
  A reference to \farg{this} duration is returned for assignment chaining.
  
  \constructor{double \farg{seconds}}
  Constructs \farg{this} duration for a time span of the given \farg{seconds}.
  A \farg{seconds} value of \code{3.25} means 3 seconds and 25 hundred's of a second.
  
  \function[const]{int64\_t}{sec}{}
  Returns the number of seconds of \farg{this} time span.
  
  \function[const]{uint32\_t}{nsec}{}
  Returns the number of nano-seconds of \farg{this} time span, e.g. the decimal part, rounded to the nano-second.
  
  \operator[const]{Duration}{-}{-}{}
  Returns the negative of \farg{this} duration.
  
  \operator[const]{bool}{==}{==}{const Duration\& \farg{that}}
  Returns \code{true} if \farg{this} duration stores the same time span as \farg{that} duration, \code{false} if not.

  \operator[const]{bool}{!=}{"!=}{const Duration\& \farg{that}}
  Returns \code{true} if \farg{this} duration stores a different time span as \farg{that} duration, \code{false} if not.
  
  \operator[const]{bool}{<}{<}{const Duration\& \farg{that}}
  Returns \code{true} if \farg{this} duration stores a time span smaller than \farg{that} duration, \code{false} if not.

  \operator[const]{bool}{>}{>}{const Duration\& \farg{that}}
  Returns \code{true} if \farg{this} duration stores a time span greater than \farg{that} duration, \code{false} if not.

  \operator[const]{bool}{<=}{<=}{const Duration\& \farg{that}}
  Returns \code{true} if \farg{this} duration stores a time span smaller or equal than \farg{that} duration, \code{false} if not.

  \operator[const]{bool}{>=}{>=}{const Duration\& \farg{that}}
  Returns \code{true} if \farg{this} duration stores a time span greater or equal than \farg{that} duration, \code{false} if not.
  
  \operator{Duration\&}{+=}{+=}{const Duration\& \farg{that}}
  Adds \farg{that} time span to \farg{this} duration and returns a reference to \farg{this} for operation chaining.
  
  \operator{Duration\&}{-=}{-=}{const Duration\& \farg{that}}
  Substracts \farg{that} time span from \farg{this} duration and returns a reference to \farg{this} for operation chaining.
  
  \operator{Duration}{+}{+}{const Duration\& \farg{lho}, const Duration\& \farg{rho}}
  Returns the time span sum of \farg{lho} and \farg{rho} durations.

  \operator{Duration}{-}{-}{const Duration\& \farg{lho}, const Duration\& \farg{rho}}
  Returns the time span difference of \farg{lho} and \farg{rho} durations.
\end{mandescription}

\end{classpage}
