%% -*- LaTeX -*-

\begin{classpage}{Handle}

A \class{Handle} is a thread safe smart pointer.
Thread safeness is achieved by means of an atomic counter.
As with other smart pointers, a handle releases data once the last handle referencing that data is destroyed.

\mansection{Synopsis}
\begin{mansynopsis}
#include <lisle/Handle>

template <typename T>
class Handle
{
public:
  ~Handle ();
  Handle (T* data = 0);
  Handle (const Handle& that);
  Handle& operator = (const Handle& that)
  operator T* ();
  operator T* () const;
  T* operator -> ();
  T* operator -> ();
};
\end{mansynopsis}

\mansection{Description}
\begin{mandescription}
  \destructor
  Destroys \farg{this} handle,
  atomically decreasing the shared usage counter,
  and eventually releasing used resources when the usage counter reaches zero.

  \constructor{T* data}
  Constructs \farg{this} handle referencing the given \farg{data}.
  If no \farg{data} is specified a handle referencing \code{NULL} is created.
  
  \constructor{const Handle\& that}
  Constructs \farg{this} handle from \farg{that} handle.
  Both handles reference the same data,
  and the shared usage counter is increased atomically.

  \operator{Handle\&}{=}{=}{const Handle\& that}
  Assigns \farg{that} handle to \farg{this} handle.
  If both handles are the same then the operation has no effect.
  Otherwise \farg{this} handle is first ``cleaned'' (dereferenced, with eventual data release),
  then \farg{that} handle is cloned into \farg{this} handle,
  and the shared usage counter is increased atomically.

  \operator{}{T*}{T*}{}
  Returns the pointer to the data stored in \farg{this} handle.
  \operator[const]{}{T*}{const T*}{}
  Returns the pointer to the data stored in \farg{this} handle.

  \operator{T*}{->}{-$>$}{}
  Returns the pointer to the data stored in \farg{this} handle, giving
  access to data and function members if \code{T} is a structure or a
  class.
  \operator[const]{T*}{->}{-$>$}{}
  Returns the pointer to the data stored in \farg{this} handle, giving
  access to data and function members if \code{T} is a structure or a
  class.

\end{mandescription}

\end{classpage}
