%% -*- LaTeX -*-

\input{preamble}

\begin{document}
\dominitoc

%==============================================================================
\begin{mantitlepage}
  \title{%
    \vspace*{13ex}
    {\Huge \bf \lisle}\\
    \vspace*{7ex}
    {\huge C++ Thread Library}\\
    \vspace*{5ex}
    {\Huge Documentation}
  }
  \author{\Large The \lisle development team}
  \date{\Large \today}
\end{mantitlepage}

\newpage
\thispagestyle{empty}
\newsavebox{\mancopybox}
\newlength{\mancopyboxheight}
\newlength{\mancopyboxvspace}
\sbox{\mancopybox}{\parbox{\linewidth}{%
\hrule
\vspace*{3ex}
Copyright \copyright\ 2002--2013, The \lisle development team.
Permission is granted to copy, distribute and/or modify this document
under the terms of the GNU Free Documentation License, Version 1.2 or
any later version published by the Free Software Foundation; with no
Invariant Sections, no Front-Cover Texts, and no Back-Cover Texts.  A
copy of the license is included in the appendix entitled ``Terms and
Conditions'', section ``Document Usage'' (Appendix~\manref{app:FDL}).
\vspace*{3ex}
\hrule
}}
\settototalheight{\mancopyboxheight}{\usebox{\mancopybox}}
\setlength{\mancopyboxvspace}{\textheight}
\addtolength{\mancopyboxvspace}{-\mancopyboxheight}
\vspace*{\mancopyboxvspace}
\noindent
\usebox{\mancopybox}

\input{postamble}
%------------------------------------------------------------------------------

%==============================================================================
\chapter{Introduction}
\label{cha:Introduction}

\lisle is a cross platform object-oriented C++ thread library. The
POSIX thread model and definitions were chosen as design template for
\lisle, but with C++ extensions and features use in mind. \lisle
is more than a C++ wraper around native thread APIs. Currently
\lisle has been ported to POSIX and Win32 native threads.

This library features cancellable and suspendable threads, and various
synchronization devices. This includes semaphores, mutexes, condition
variables, barriers, and other more complex components.
Chapter~\ref{cha:Synchronization-Devices} gives the complete list and
APIs for \lisle synchronization devices.

Existing thread APIs do not provide a consistent and portable means
for exercising control over concurrent threads of execution. For
instance, each platform has its own specialized methods for error
handling, thread cancellation and termination. \lisle includes an
elegant method of safely terminating threads without the complications
of using cancellation handlers or other similar
constructs. Chapter~\ref{cha:Thread-Management} decribes the
primitives and APIs for \lisle thread management.

\lisle can detect various concurrency and synchronization faults in
programs and signals them through C++ exceptions. All synchronization
devices are protected against destruction while at least one thread
still owns it. The library can also detect and signal deadlock
situations. \lisle assists developers as much as possible in order
to provide the best as possible final concurrent
software. Chapter~\ref{cha:Exceptions} lists all exceptions that can
be thrown by \lisle.
%------------------------------------------------------------------------------

%==============================================================================
\chapter{Design Choices}
\label{cha:Design-Choices}

\manminitoc
\noindent
As in every real world engineering project, \lisle{} was designed and
implemented with compromises to the original ideal software that we
had in mind. In this chapter we explain and justify the design and
implementation choices we made for \lisle{}. This chapter is not a
justification for a bad design, but to explain what choices were made
according to the limitations found in current state of the art
computer technology, languages, and third party libraries, on top of
which \lisle{} is built.

\section{Cancellation}
\label{sec:Design-Cancellation}

\lisle provides synchronous thread cancellation. You may wonder why
despite POSIX thread provides asynchronous thread cancellation
\lisle doesn't. This is because the choice was made to impose no
cancellation handler management to the developpers, but to use plain
C++ destruction mechanisms to clean up when a thread honors a
cancellation request.

Indeed, C++ comes with object destructors which are automatically
called when an object exits a scope block. It is a very reliable
mechanism one can build on. Every time an object gets out of focus,
either by regular scope exit or when an exception is thrown, the
object's destructor is called. It is in the destructor that you
implement object cleanup and resources release.

When a \lisle thread honors a cancellation request it uses the
regular C++ stack unwinding and automatic destructor calls. In fact,
in \lisle thread cancellation is implemented by means of a cancel
exception throwing. The advantage is that the aformentioned C++ stack
unwinding mechanism is invoked to cleanup, the drawback being some
restrictions on exception specifications and catching.

Functions where a cancellation request can be honored {\bf can not}
have an explicit C++ exception specification. Indeed, the \lisle's
internal exceptions used to cancel and/or exit a thread would never
match your exception specifications since you don't know the names of
\lisle's internal exceptions. Specifing C++ exceptions in the
cancellable path of a thread will lead to an unexpected exception
being thrown, what is not what you expect.

Furthermore in functions where a cancellation request can be honored
no generic catching (with \code{catch(...)}) can be used. Using a
generic exception catching would catch the \lisle thread management
exception as well as all other exceptions, without filtering. Thus you
would break \lisle's thread management chain and never be informed
what happened to your thread. Plus the thread's internal state
descriptor would no longer be coherent with the thread's actual state.

Using the C++ exception mechanism to implement thread cancellation
forbids the handling of asynchronous cancellation requests. Indeed, it
is not possible to throw a C++ exception in a signal handler (Unix) or
very unsafe in an event handler (Win32). Moreover, imagine what would
happen if the thread to cancel is in a function (say \code{malloc}).
There is no way to predict what would happen when a program jumps out
of a C function without leting this function terminate properly.

Let's take \code{malloc} as an example. This function reserves some
memory and returns a pointer to the memory block. It will first place
a system call to get a memory block, then do some error checking, and
finally assign and return a pointer to the memory block. Imagine the
thread calling malloc is cancelled between the memory reservation
system call and the error checking. The pointer to return would never
be assigned, and we would never know if the memory reservation
succeeded or failed. The process would continue to run, but its state
would no longer be 100\% defined, which is not to recommend for a
state machine (as every piece of software is).
%------------------------------------------------------------------------------

%==============================================================================
\chapter{Synchronization Devices}
\label{cha:Synchronization-Devices}

\manminitoc
\noindent
The synchronization devices is a set of C++ classes used to synchronize
threads. Thread synchronization is used to avoid data race conditions,
to provide flow control mechanisms, and much more.

\input{Mutex}
\input{Retex}
\input{Acquirer}
\input{Releaser}
\input{Semaphore}
\input{Condition}
\input{Event}
\input{Shorex}
\input{Barrier}
%------------------------------------------------------------------------------

%==============================================================================
\chapter{Thread Mangement}
\label{cha:Thread-Management}

\manminitoc
\noindent
The thread management is a set of C++ classes and functions to handle
threads. Thread management provides tools to start, stop, identify,
etc, threads.

\input{create}
\input{self}
\input{Thread}
\input{Thrid}
\input{Once}
\input{Local}
%------------------------------------------------------------------------------

%==============================================================================
\chapter{Miscellaneous}
\label{cha:Miscellaneous}

\manminitoc
\noindent
Helper classes.

\input{Handle}
\input{Anondle}
\input{Countic}
\input{Duration}
%------------------------------------------------------------------------------

%==============================================================================
\chapter{Exceptions}
\label{cha:Exceptions}

\manminitoc
\noindent

\section{Resource}
\label{sec:Exceptions.Resource}
A \class{resource} exception is thrown whenever there are not enough system resources left to create an instance of a thread related item.
Expect a \class{resource} exception to be thrown by a constructor.

\section{Permission}
\label{sec:Exceptions.Permission}
A \class{permission} exception is thrown whenever the program doesn't have permission to perform a given operation.
Expect a \class{permission} exception to be thrown by a destructor, or by a setting on a thread the operating system wouldn't allow.

\section{Deadlock}
\label{sec:Exceptions.Deadlock}
Expect a \class{deadlock} exception when \lisle detects an operation that would lock a thread in a state from which it can't exit.
For example self joining a thread would deadlock.
An attempt to relock a mutex will also throw a \class{deadlock} exception.

\section{Overflow}
\label{sec:Exceptions.Overflow}
Expect an \class{overflow} exception when a post operation would overflow a semaphore count.

\section{Timeout}
\label{sec:Exceptions.Timeout}
A \class{timeout} exception is thrown whenever a timed wait terminates on the duration condition.
Expect a \class{timeout} exception on all timed waits.

\section{Virthread}
\label{sec:Exceptions.Virthread}
A \class{virthread} exception is thrown whenever a null function thread creation is attempted.

\section{Internal}
\label{sec:Exceptions.Internal}
\lisle uses exceptions for thread termination and cancellation.
Using exceptions ensures that the stack is unwound correctly and that all used resources are released properly.
Internal exceptions all derive from the \code{threption} base class.
It is mandatory to let \code{threption} exceptions flow freely without being caught.
\\
Thus a
\\
\indent \code{catch~(...)}
\\
clause must be preceded by a
\\
\indent \code{catch~(threption\&)~\{throw;\}}
\\
clause for thread cancellation and termination to work.
The correct catch all is thus:
\\
\indent \code{catch~(threption\&)~\{throw;\}}
\\
\indent \code{catch~(...)}
%------------------------------------------------------------------------------

%==============================================================================
\appendix

\newpage
\chapter{Terms and Conditions}
\label{app:Terms}

\section{Library Usage}
\label{app:LGPL}
The \lisle thread C++ library is distributed under the terms and
conditions of the GNU library general public license. The following
text describes the terms and conditions for copying, distribution and
modification of \lisle. In the following text ``library'' refers to
the ``\lisle C++ thread library''.
\vspace*{5ex}
\input{LGPL}

\newpage
\section{Document Usage}
\label{app:FDL}
The \lisle thread C++ library documentation is distributed under the
terms and conditions of the GNU free documentation license. The
following text describes the terms and conditions for copying,
distribution and modification of the \lisle documentation. In the
following text ``document'' refers to the ``\lisle C++ thread library
documentation'' (this document).
\input{FDL}
%------------------------------------------------------------------------------

%==============================================================================
%------------------------------------------------------------------------------

\input{index}

\end{document}
