%% -*- LaTeX -*-

\begin{classpage}{Semaphore}

Semaphores are counters for resources shared between threads. The
basic operations on semaphores are: increment the counter atomically,
and wait until the counter is non-null and decrement it atomically.

\mansection{Synopsis}
\begin{mansynopsis}
#include <lisle/Semaphore>

namespace lisle {
class Semaphore
{
public:
  ~Semaphore ()
    throw (permission);
  Semaphore (size_t value=0)
    throw (resource);
  static size_t max ()
    throw ();
  size_t value () const
    throw ();
  bool trywait ()
    throw ();
  void wait ()
    throw ();
  void post ()
    throw (overflow);
private:
  // @textnit$Disable cloning?
  Semaphore (const Semaphore&);
  Semaphore& operator = (const Semaphore&);
};
}
\end{mansynopsis}

\mansection{Description}
\begin{mandescription}
  \destructor
  Destroys \farg{this} semaphore, freeing all resources it might
  hold. No threads should be waiting on \farg{this} semaphore at the
  time of destruction.
  \begin{exception}
    \item[permission] is thrown if there are blocked
      threads waiting on \farg{this} semaphore.
  \end{exception}

  \constructor{size\_t \farg{value} = 0}
  Constructs \farg{this} semaphore. The count associated with
  \farg{this} semaphore is initially set to the given
  \farg{value}. If no value is given the count is set to zero.
  \begin{exception}
    \item[resource] is thrown if there are not
      enough system resources to create \farg{this} new semaphore.
  \end{exception}

  \function[static]{size\_t}{max}{}
  Returns the maximum count a semaphore can store.

  \function[const]{size\_t}{value}{}
  Returns the current count of \farg{this} semaphore.

  \function{bool}{trywait}{}
  This function is a non-blocking variant of 
  \code{wait()}. If \farg{this} semaphore has a non-zero
  count, the count is atomically decreased and \code{true} is
  returned, else \code{false} is returned.

  \function{void}{wait}{}
  Suspends the calling thread until \farg{this} semaphore has non-zero count.
  The count of \farg{this} semaphore is atomically decreased on wait termination.
  
  \function{void}{post}{}
  Atomically increases the count of \farg{this} semaphore.
  \begin{exception}
    \item[overflow] is thrown if after incrementation,
      \farg{this} semaphore value would exceed the system's maximum
      value for semaphore count. The semaphore count is left
      unchanged in this case. The system's maximum semaphore count
      value is system dependent.
  \end{exception}
\end{mandescription}

\mansection{Cancellation}
\code{Semaphore::wait()} is a cancellation point.

\mansection{Async-Signal Safety}
  The semaphore functions are not async-signal safe. What this means is
  that they should not be called from a signal handler.

\end{classpage}
