%% -*- LaTeX -*-

\begin{classpage}{Thread::Attribute}

The \code{Thread::Attribute} class is a thread behaviour
descriptor. Objects of this class are used as second (optional)
argument to the \code{Thread::create} function. They have no other use
in \lisle{}. The class is a container which stores:

\begin{itemize}
  \item The thread's startup join state. A thread is either in
    \code{Joinable} or \code{Detached} state.\\
    In the joinable state, another thread can synchronize on the
    thread termination and recover its termination code using
    \code{Thread::Id::join()} but some of the thread resources are
    kept allocated after the thread terminates, and reclaimed only
    when another thread performs a \code{Thread::Id::join()} on that
    thread.\\
    In the detached state, the thread resources are immediately freed
    when it terminates, and \code{Thread::Id::join()} cannot be used
    to synchronize on the thread termination.\\
    A thread created in the joinable state can later be put in the
    detached state using \code{Thread::Id::detach()}.
  \item The thread's scheduling
    policy. Table~\manref{tab:Thread-Scheduling} shows the available
    scheduling policies.
    \begin{table}[htbp]
      \centering
      \begin{tabular}[h]{|l|p{0.6\linewidth}|}
        \hline
        \textbf{Schedule} & \textbf{Description} \\
        \hline
        \code{Inherit} &
        The thread's scheduling policy is inherited from the calling
        thread. \\
        \code{Parent} &
        Alias for \code{Inherit}. \\
        \hline
        \code{Regular} &
        Regular non-realtime scheduling. This is the scheduling policy
        available for regular users. \\
        \code{Other} &
        Alias for \code{Regular}. \\
        \hline
        \code{Circular} &
        Realtime round-robin scheduling. This scheduling policy
        requires superuser privileges. \\
        \hline
        \code{Fifo} &
        Realtime first in first out scheduling. This scheduling policy
        requires superuser privileges. \\
        \hline
      \end{tabular}
      \caption{Thread scheduling policies}
      \label{tab:Thread-Scheduling}
    \end{table}
\end{itemize}

\let\savedmanlayout=\manlayout
\renewcommand{\manlayout}{vcompact}

\mansection{Synopsis}
\begin{mansynopsis}
#include <lisle/Thread.Attribute>

class Thread::Attribute
{
public:
  enum State { Joinable, Detached };
  enum Schedule { Inherit, Regular, Circular, Fifo, 
                  Parent=Inherit, Other=Regular };
  enum Priority { Lazy, Lowest, Low, Normal, 
                  High, Highest, Critical };
  ~Attribute ();
  Attribute (State state = Joinable,
             Schedule schedule = Regular,
             Priority priority = Normal);
  Attribute (const Attribute& attribute);
  Attribute& operator = (const Attribute& attribute);
  State state () const;
  Schedule schedule () const;
  Priority priority () const;
  void state (State val);
  void schedule (Schedule val);
  void priority (Priority val);
};
\end{mansynopsis}

\mansection{Description}
\begin{mandescription}
  \destructor
  Destroys \farg{this} thread attribute.

  \constructor{%
    Attribute::State \farg{state} = Joinable,
    Attribute::Schedule \farg{schedule} = Regular,
    Attribute::Priority \farg{priority} = Normal}
  Constructs \farg{this} thread attribute. Optional arguments
  \farg{state}, \farg{schedule}, and \farg{priority} can be given to
  construct \farg{this} thread attribute with the given \farg{state},
  \farg{schedule}, and \farg{priority} initial values.

  \constructor{const Thread::Attribute\& \farg{attribute}}
  Constructs \farg{this} thread attribute from the given
  \farg{attribute}. All data stored in \farg{attribute} are cloned
  into \farg{this} thread attribute.

  \operator{Thread::Attribute\&}{=}{=}{const Thread::Attribute\&
  \farg{attribute}}
  Assigns the rvalue \farg{attribute} to \farg{this} thread
  attribute. All data stored in the rvalue \farg{attribute} are cloned
  into \farg{this} thread attribute. A reference to \farg{this}
  thread attribute is returned for assignment operation chaining.

  \function[const]{Attribute::State}{state}{}
  Returns the thread join state stored in \farg{this} thread
  attribute.

  \function[const]{Attribute::Schedule}{schedule}{}
  Returns the thread scheduling policy stored in \farg{this} thread
  attribute.

  \function[const]{Attribute::Priority}{priority}{}
  Returns the thread priority stored in \farg{this} thread attribute.

  \function{void}{state}{Attribute::State \farg{val}}
  Sets the thread join state field of \farg{this} thread attribute to
  the given \farg{val}ue.

  \function{void}{schedule}{Attribute::Schedule \farg{val}}
  Sets the thread scheduling policy of \farg{this} thread attribute to
  the given \farg{val}ue.

  \function{void}{priority}{Attribute::Priority \farg{val}}
  Sets the thread priority of \farg{this} thread attribute to the
  given \farg{val}ue.
\end{mandescription}

\renewcommand{\manlayout}{\savedmanlayout}

\end{classpage}
